---
title: "Introduction to vitorcid"
description: >
  Learn how to get started with the basics of vitorcid.
author: "vitorcid team"
vignette: >
  %\VignetteIndexEntry{vitorcid}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Quick summary

The `vitorcid` package allows you to generate a CV based on your ORCID profile.

# Installation

You can install the package using remotes in the following way:

```         
remotes::install_github("https://github.com/gladkia/vitorcid.git", ref = "main")
```

# Authentication

Take care of the authentication requirements with three steps:

1.  Authenticate with orcid.org as described [here](https://github.com/ropensci-archive/rorcid/blob/master/vignettes/authentication.Rmd).

2.  Create an environment variable 'ORCID TOKEN'. Use the value obtained from the previous step.

```{r, eval = FALSE}
Sys.setenv(ORCID_TOKEN = "__your_token__")

```

3.  Create an environment variable with your 'ORCID ID'.

```{r, eval = FALSE}
Sys.setenv(ORCID_ID = "__your_orcid_id__")

```

If you have a problem with authentication, you can also try this path:

1.  restart session in R Studio

2.  create an environment variables with your 'ORCID_ID' and 'ORCID_TOKEN' as above

3.  sign your ORCID_ID to 'orcid'

4.  complete authentication your profile using 'rorcid::orcid_auth()'

    \*if you change your token use 'rorcid::orcid_auth(reauth = TRUE)'

5.  load package using 'library("vitorcid")'

# CV generation - fast path

1.  Create an account on <https://orcid.org/>.

This is an example of a completed profile: [link](https://orcid.org/0000-0002-7059-6378/print).

**Employment** and **Education** sections are required.

**Websites** and **Social Links** are encouraged but not mandatory.

2.  Generate your CV:

```{r, eval = FALSE}
vitorcid::get_cv("CV")
```

3.  Review CV.pdf (generated CV). If some corrections are needed you can do them in two ways:

-   update the data at orcid.org and rerun `get_cv`
-   edit the template (CV.Rmd) and knit it (e.g. from within the Rstudio)

# Use cases

## Customizing CV data with JSON file

Sometimes one might want to customize the CV data. There are three general cases: \* adding the data unavailable from orcid.org \* overwriting the data fetched from orcid.org \* adding the data not provided at orcid.org

#### Header data

Currently, there are two header entries that can be provided only via JSON file: 'position' and 'address'. Here is the example JSON file with both entries defined:

```{r}
j_path <- system.file(package = "vitorcid", "json_examples/orcid_0000-0002-7059-6378_header_data.json")
jsonlite::toJSON(jsonlite::fromJSON(j_path), pretty = TRUE)
```

Sometimes, user might want to update the email or profile picture:

```{r}
j_path <- system.file(package = "vitorcid", "json_examples/orcid_0000-0002-7059-6378_email.json")
jsonlite::toJSON(jsonlite::fromJSON(j_path), pretty = TRUE)

j_path <- system.file(package = "vitorcid", "json_examples/orcid_0000-0002-7059-6378_profilepic.json")
jsonlite::toJSON(jsonlite::fromJSON(j_path), pretty = TRUE)
```

One can use the JSON data while getting the latest CV in the following way:

```{r, eval = FALSE}
vitorcid::get_cv(json_path = j_path)
```

### Non-header data

One is not able to provide details about specific employment or education entries at the orcid.org. Here is the example of defining such details for the user with ORCID ID: "0000-0002-7059-6378". In his case there are four employment and two education entries (see details [here](https://orcid.org/0000-0002-7059-6378/print).

```{r}
# defining details with idx (counting from the top to the bottom)
j_path <- system.file(package = "vitorcid", "json_examples/orcid_0000-0002-7059-6378_why_idx.json")
jsonlite::toJSON(jsonlite::fromJSON(j_path), pretty = TRUE)

# defining details with put-code(s) from orcid.org
# each put-code refers to the given record from education/employment
j_path <- system.file(package = "vitorcid", "json_examples/orcid_0000-0002-7059-6378_why_put-code.json")
jsonlite::toJSON(jsonlite::fromJSON(j_path), pretty = TRUE)
```

One can use the JSON data while getting the latest CV in the following way:

```{r, eval = FALSE}
vitorcid::get_cv(json_path = j_path)
```

# SessionInfo {.unnumbered}

```{r sessionInfo}
sessionInfo()
```
