---
title: "Introduction to vitorcid"
description: >
  Learn how to get started with the basics of vitorcid.
author: "vitorcid team"
vignette: >
  %\VignetteIndexEntry{vitorcid}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(vitorcid)
```

# Overview
To be added soon.

# Use cases

## Customizing CV data with JSON file

Sometimes one might want to customize the CV data. There are three general cases:
* adding the data unavailable from orcid.org
* overwriting the data fetched from orcid.org 
* adding the data not provided at orcid.org

####  Header data
Currently, there are two header entries that can be provided only via JSON file: 'position' and 'address'. Here is the example JSON file with both entries defined: 
```{r}
j_path <- system.file(package = "vitorcid", "json_examples/orcid_0000-0002-7059-6378_header_data.json")
jsonlite::toJSON(jsonlite::fromJSON(j_path), pretty = TRUE)
```

Sometimes, user might want to update the email or profile picture:
```{r}
j_path <- system.file(package = "vitorcid", "json_examples/orcid_0000-0002-7059-6378_email.json")
jsonlite::toJSON(jsonlite::fromJSON(j_path), pretty = TRUE)

j_path <- system.file(package = "vitorcid", "json_examples/orcid_0000-0002-7059-6378_profilepic.json")
jsonlite::toJSON(jsonlite::fromJSON(j_path), pretty = TRUE)
```

One can use the JSON data while getting the latest CV in the following way:
```{r, eval = FALSE}
vitorcid::get_cv(json_path = j_path)
```


### Non-header data
One is not able to provide details about specific employment or education entries at the orcid.org. Here is the example of defining such details for the user with ORCID ID: "0000-0002-7059-6378". In his case there are four employment and two education entries (see details [here]( https://orcid.org/0000-0002-7059-6378/print).

```{r}
# defining details with idx (counting from the top to the bottom)
j_path <- system.file(package = "vitorcid", "json_examples/orcid_0000-0002-7059-6378_why_idx.json")
jsonlite::toJSON(jsonlite::fromJSON(j_path), pretty = TRUE)

# defining details with put-code(s) from orcid.org
# each put-code refers to the given record from education/employment
j_path <- system.file(package = "vitorcid", "json_examples/orcid_0000-0002-7059-6378_why_put-code.json")
jsonlite::toJSON(jsonlite::fromJSON(j_path), pretty = TRUE)
```

One can use the JSON data while getting the latest CV in the following way:
```{r, eval = FALSE}
vitorcid::get_cv(json_path = j_path)
```

# SessionInfo {-}

```{r sessionInfo}
sessionInfo()
```
